Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2023-03-13 products/paper/main.qmd
Forgot slight edit to the previous footnote

[^yeargrade]: The supplementary materials provide, for each specification, the BIC scores and marginal probabilities of being clearly behind expected grade for each racial group. The marginal probabilities for each racial group are almost identical across specifications, indicating that results are not driven by the modeling choice made here.

>>>>

[^yeargrade]: The supplementary materials provide, for each model specification, the BIC scores and marginal probabilities of being clearly behind expected grade for each racial group. The marginal probabilities for each racial group are almost identical across specifications, indicating that results are not driven by the modeling choice made here.
